---
title: ""
output:
  html_document:
    theme: null
    self_contained: true
    css: null
params:
  team: "Unknown Team"
  pitcher_hand: "Right"
  dates: !r c(Sys.Date() - 30, Sys.Date())
  batters: NULL
  batter_data: NULL
  batter_notes: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center")
library(tidyverse)
library(kableExtra)
library(viridisLite)
library(gridExtra)

# Source helper functions if not already loaded
if (!exists("generate_swingmiss_heatmap")) {
  # Define inline versions for standalone rendering

  pitch_type_map <- list(
    "4SM" = c("Fastball", "Four-Seam", "FourSeam", "FourSeamFastBall"),
    "2SM" = c("Sinker", "Two-Seam", "TwoSeam", "TwoSeamFastBall"),
    "CT" = c("Cutter"),
    "CB" = c("Curveball", "Curve"),
    "SL" = c("Slider", "Sweeper"),
    "CH" = c("Changeup", "ChangeUp", "Splitter")
  )

  map_pitch_type <- function(pitch_type) {
    if (is.na(pitch_type) || is.null(pitch_type)) return(NA_character_)
    for (abbrev in names(pitch_type_map)) {
      if (pitch_type %in% pitch_type_map[[abbrev]]) {
        return(abbrev)
      }
    }
    pitch_type
  }

  generate_swingmiss_heatmap <- function(df, pitch_type, title = NULL) {
    plot_data <- df |>
      filter(pitch_type_abbrev == pitch_type & pitchcall == "StrikeSwinging") |>
      filter(!is.na(platelocside) & !is.na(platelocheight))

    if (is.null(title)) title <- paste0("S/M ", pitch_type)

    if (nrow(plot_data) < 3) {
      return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 2, color = "#888") +
             theme_void() + labs(title = title) +
             theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold")))
    }

    cols <- viridisLite::turbo(256)
    cols[1] <- "white"

    ggplot(plot_data, aes(x = platelocside, y = platelocheight)) +
      stat_density_2d(aes(fill = after_stat(ndensity)), geom = "raster", contour = FALSE, h = c(0.55, 0.55), n = 50) +
      scale_fill_gradientn(colors = cols, guide = "none") +
      annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5, fill = NA, color = "black", linewidth = 0.4) +
      coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
      labs(title = title) +
      theme_void() +
      theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold"), plot.margin = margin(1,1,1,1))
  }

  generate_slg_heatmap_batter <- function(df, pitch_type, title = NULL) {
    plot_data <- df |>
      filter(pitch_type_abbrev == pitch_type & pitchcall == "InPlay") |>
      filter(playresult %in% c("Single", "SIngle", "Double", "Triple", "triple", "HomeRun", "Homerun")) |>
      filter(!is.na(platelocside) & !is.na(platelocheight))

    if (is.null(title)) title <- paste0("AVG ", pitch_type)

    if (nrow(plot_data) < 3) {
      return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 2, color = "#888") +
             theme_void() + labs(title = title) +
             theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold")))
    }

    cols <- viridisLite::turbo(256)
    cols[1] <- "white"

    ggplot(plot_data, aes(x = platelocside, y = platelocheight)) +
      stat_density_2d(aes(fill = after_stat(ndensity)), geom = "raster", contour = FALSE, h = c(0.55, 0.55), n = 50) +
      scale_fill_gradientn(colors = cols, guide = "none") +
      annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5, fill = NA, color = "black", linewidth = 0.4) +
      coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
      labs(title = title) +
      theme_void() +
      theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold"), plot.margin = margin(1,1,1,1))
  }

  generate_exitvelo_heatmap <- function(df, title = "EXITVELO") {
    plot_data <- df |>
      filter(pitchcall == "InPlay" & !is.na(exitspeed)) |>
      filter(!is.na(platelocside) & !is.na(platelocheight))

    if (nrow(plot_data) < 3) {
      return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 2, color = "#888") +
             theme_void() + labs(title = title) +
             theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold")))
    }

    cols <- viridisLite::turbo(256)
    cols[1] <- "white"

    ggplot(plot_data, aes(x = platelocside, y = platelocheight)) +
      stat_density_2d(aes(fill = after_stat(ndensity)), geom = "raster", contour = FALSE, h = c(0.55, 0.55), n = 50) +
      scale_fill_gradientn(colors = cols, guide = "none") +
      annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5, fill = NA, color = "black", linewidth = 0.4) +
      coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
      labs(title = title) +
      theme_void() +
      theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold"), plot.margin = margin(1,1,1,1))
  }

  generate_popup_heatmap <- function(df, title = "POPUP") {
    plot_data <- df |>
      filter(pitchcall == "InPlay" & !is.na(angle)) |>
      filter(angle > 50) |>
      filter(!is.na(platelocside) & !is.na(platelocheight))

    if (nrow(plot_data) < 3) {
      return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 2, color = "#888") +
             theme_void() + labs(title = title) +
             theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold")))
    }

    cols <- viridisLite::turbo(256)
    cols[1] <- "white"

    ggplot(plot_data, aes(x = platelocside, y = platelocheight)) +
      stat_density_2d(aes(fill = after_stat(ndensity)), geom = "raster", contour = FALSE, h = c(0.55, 0.55), n = 50) +
      scale_fill_gradientn(colors = cols, guide = "none") +
      annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5, fill = NA, color = "black", linewidth = 0.4) +
      coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
      labs(title = title) +
      theme_void() +
      theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold"), plot.margin = margin(1,1,1,1))
  }

  generate_2k_miss_heatmap <- function(df, title = "2K MISS") {
    plot_data <- df |>
      filter(strikes == 2 & pitchcall == "StrikeSwinging") |>
      filter(!is.na(platelocside) & !is.na(platelocheight))

    if (nrow(plot_data) < 3) {
      return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 2, color = "#888") +
             theme_void() + labs(title = title) +
             theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold")))
    }

    cols <- viridisLite::turbo(256)
    cols[1] <- "white"

    ggplot(plot_data, aes(x = platelocside, y = platelocheight)) +
      stat_density_2d(aes(fill = after_stat(ndensity)), geom = "raster", contour = FALSE, h = c(0.55, 0.55), n = 50) +
      scale_fill_gradientn(colors = cols, guide = "none") +
      annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5, fill = NA, color = "black", linewidth = 0.4) +
      coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
      labs(title = title) +
      theme_void() +
      theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold"), plot.margin = margin(1,1,1,1))
  }

  generate_2k_take_heatmap <- function(df, title = "2K TAKE") {
    plot_data <- df |>
      filter(strikes == 2 & pitchcall == "StrikeCalled") |>
      filter(!is.na(platelocside) & !is.na(platelocheight))

    if (nrow(plot_data) < 3) {
      return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 2, color = "#888") +
             theme_void() + labs(title = title) +
             theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold")))
    }

    cols <- viridisLite::turbo(256)
    cols[1] <- "white"

    ggplot(plot_data, aes(x = platelocside, y = platelocheight)) +
      stat_density_2d(aes(fill = after_stat(ndensity)), geom = "raster", contour = FALSE, h = c(0.55, 0.55), n = 50) +
      scale_fill_gradientn(colors = cols, guide = "none") +
      annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5, fill = NA, color = "black", linewidth = 0.4) +
      coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
      labs(title = title) +
      theme_void() +
      theme(plot.title = element_text(hjust = 0.5, size = 6, face = "bold"), plot.margin = margin(1,1,1,1))
  }
}

# Highlight colors
highlight_colors <- list(
  "none" = "transparent",
  "yellow" = "#fef08a",
  "green" = "#bbf7d0",
  "red" = "#fecaca",
  "blue" = "#bfdbfe",
  "orange" = "#fed7aa",
  "purple" = "#e9d5ff"
)

# Count labels
count_labels <- c("0-0", "RISP", "0-1", "1-0", "1-1", "2-0", "2-1", "3-1", "0-2", "1-2", "2-2", "3-2")

# Null coalescing operator
`%||%` <- function(x, y) if (is.null(x) || length(x) == 0 || (is.character(x) && x == "")) y else x
```

<style>
/* Print-optimized compact layout */
body {
  font-family: Arial, sans-serif;
  font-size: 8px;
  margin: 0;
  padding: 5px;
  max-width: 100%;
}

@media print {
  @page { size: letter landscape; margin: 0.2in; }
  body {
    -webkit-print-color-adjust: exact;
    print-color-adjust: exact;
    font-size: 7px;
    padding: 0;
    margin: 0;
  }
  .batter-section { page-break-inside: avoid; }
}

.header-box {
  background: #1a365d;
  color: white;
  padding: 8px 15px;
  margin-bottom: 10px;
  border-radius: 4px;
}
.header-box h1 { margin: 0; font-size: 16px; }
.header-box .subtitle { font-size: 10px; opacity: 0.9; }

.batter-section {
  border: 1px solid #e2e8f0;
  border-radius: 6px;
  padding: 8px;
  margin-bottom: 12px;
  background: #fafafa;
}

.batter-header {
  background: #2d3748;
  color: white;
  padding: 5px 10px;
  margin-bottom: 8px;
  border-radius: 3px;
  font-size: 12px;
  font-weight: bold;
}

.heatmap-row {
  display: flex;
  gap: 3px;
  margin-bottom: 5px;
}

.heatmap-cell {
  flex: 1;
  text-align: center;
}

.heatmap-label {
  font-size: 7px;
  font-weight: bold;
  margin-bottom: 1px;
}

.count-row {
  display: flex;
  gap: 2px;
  margin-bottom: 8px;
  flex-wrap: wrap;
}

.count-box {
  flex: 0 0 55px;
  text-align: center;
  padding: 3px;
  border: 1px solid #ddd;
  border-radius: 3px;
  font-size: 8px;
}

.count-label {
  font-weight: bold;
  margin-bottom: 2px;
}

.count-values {
  display: flex;
  gap: 2px;
  justify-content: center;
}

.count-value {
  background: #f0f0f0;
  padding: 1px 4px;
  border-radius: 2px;
  min-width: 20px;
}

.images-row {
  display: flex;
  gap: 5px;
  margin-bottom: 8px;
}

.image-cell {
  flex: 1;
  text-align: center;
}

.image-placeholder {
  height: 50px;
  background: #f5f5f5;
  border: 1px dashed #ccc;
  border-radius: 3px;
  display: flex;
  align-items: center;
  justify-content: center;
  font-size: 7px;
  color: #888;
}

.image-cell img {
  max-height: 50px;
  max-width: 100%;
  border: 1px solid #ddd;
  border-radius: 3px;
}

.stats-notes-row {
  display: flex;
  gap: 10px;
}

.stats-grid {
  display: grid;
  grid-template-columns: repeat(4, 1fr);
  gap: 3px;
  flex: 0 0 200px;
}

.stat-cell {
  text-align: center;
  background: #f0f0f0;
  padding: 2px;
  border-radius: 2px;
}

.stat-label {
  font-size: 7px;
  font-weight: bold;
}

.stat-value {
  font-size: 9px;
}

.notes-box {
  flex: 1;
  background: #fffbeb;
  border: 1px solid #f6e05e;
  border-radius: 3px;
  padding: 4px;
  font-size: 8px;
}

.notes-label {
  font-weight: bold;
  color: #744210;
  font-size: 8px;
  margin-bottom: 2px;
}

.footer {
  margin-top: 10px;
  padding-top: 5px;
  border-top: 1px solid #e2e8f0;
  font-size: 7px;
  color: #718096;
  text-align: center;
}
</style>

```{r header, results='asis', echo=FALSE}
hand_text <- if(params$pitcher_hand == "Right") "vs RHP" else "vs LHP"
cat('<div class="header-box">')
cat(sprintf('<h1>%s | Hitter Scouting Report</h1>', params$team))
cat(sprintf('<div class="subtitle">%s | %s to %s</div>', hand_text, params$dates[1], params$dates[2]))
cat('</div>')
```

```{r batter-sections, results='asis', echo=FALSE, fig.height=0.8, fig.width=0.8}
if (!is.null(params$batters) && length(params$batters) > 0) {

  for (batter in params$batters) {
    df <- params$batter_data[[batter]]
    notes <- params$batter_notes[[batter]]
    if (is.null(notes)) notes <- list()

    cat('<div class="batter-section">')
    cat(sprintf('<div class="batter-header">%s</div>', batter))

    # S/M Heatmaps Row
    cat('<div class="heatmap-row">')
    for (pt in c("4SM", "2SM", "CT", "CB", "SL", "CH")) {
      cat('<div class="heatmap-cell">')
      cat(sprintf('<div class="heatmap-label">S/M %s</div>', pt))
      cat('</div>')
    }
    cat('</div>')

    # Generate S/M heatmaps
    if (!is.null(df) && nrow(df) > 0) {
      sm_plots <- lapply(c("4SM", "2SM", "CT", "CB", "SL", "CH"), function(pt) {
        generate_swingmiss_heatmap(df, pt)
      })
      print(gridExtra::grid.arrange(grobs = sm_plots, nrow = 1))
    }

    # AVG Heatmaps Row
    cat('<div class="heatmap-row">')
    for (pt in c("4SM", "2SM", "CT", "CB", "SL", "CH")) {
      cat('<div class="heatmap-cell">')
      cat(sprintf('<div class="heatmap-label">AVG %s</div>', pt))
      cat('</div>')
    }
    cat('</div>')

    # Generate AVG heatmaps
    if (!is.null(df) && nrow(df) > 0) {
      avg_plots <- lapply(c("4SM", "2SM", "CT", "CB", "SL", "CH"), function(pt) {
        generate_slg_heatmap_batter(df, pt)
      })
      print(gridExtra::grid.arrange(grobs = avg_plots, nrow = 1))
    }

    # Count boxes row
    cat('<div class="count-row">')
    for (count in count_labels) {
      count_data <- notes$count_data[[count]]
      val1 <- if (!is.null(count_data) && length(count_data) >= 1) count_data[[1]] %||% "" else ""
      val2 <- if (!is.null(count_data) && length(count_data) >= 2) count_data[[2]] %||% "" else ""

      highlight <- notes$highlights[[count]] %||% "none"
      bg_color <- highlight_colors[[highlight]] %||% "transparent"

      cat(sprintf('<div class="count-box" style="background: %s;">', bg_color))
      cat(sprintf('<div class="count-label">%s</div>', count))
      cat('<div class="count-values">')
      cat(sprintf('<div class="count-value">%s</div>', val1))
      cat(sprintf('<div class="count-value">%s</div>', val2))
      cat('</div>')
      cat('</div>')
    }
    cat('</div>')

    # Images + auto-generated heatmaps row
    cat('<div class="images-row">')

    # Manual upload images
    for (img_info in list(
      list(id = "box", label = "BOX"),
      list(id = "contact_point", label = "CONTACT"),
      list(id = "spray_chart", label = "SPRAY"),
      list(id = "risp_gb", label = "RISP GB")
    )) {
      img_url <- notes[[paste0("img_", img_info$id)]] %||% ""
      cat('<div class="image-cell">')
      cat(sprintf('<div class="heatmap-label">%s</div>', img_info$label))
      if (img_url != "") {
        cat(sprintf('<img src="%s" />', img_url))
      } else {
        cat('<div class="image-placeholder">-</div>')
      }
      cat('</div>')
    }

    # Auto-generated heatmaps labels
    for (label in c("EXITVELO", "POPUP", "2K MISS", "2K TAKE")) {
      cat('<div class="image-cell">')
      cat(sprintf('<div class="heatmap-label">%s</div>', label))
      cat('</div>')
    }
    cat('</div>')

    # Generate auto heatmaps
    if (!is.null(df) && nrow(df) > 0) {
      auto_plots <- list(
        generate_exitvelo_heatmap(df),
        generate_popup_heatmap(df),
        generate_2k_miss_heatmap(df),
        generate_2k_take_heatmap(df)
      )
      # Add empty plots for manual images
      empty_plot <- ggplot() + theme_void()
      all_plots <- c(list(empty_plot, empty_plot, empty_plot, empty_plot), auto_plots)
      print(gridExtra::grid.arrange(grobs = all_plots, nrow = 1))
    }

    # Stats and notes row
    cat('<div class="stats-notes-row">')

    # Stats grid
    cat('<div class="stats-grid">')
    for (stat in list(
      list(id = "slg", label = "SLG"),
      list(id = "run", label = "RUN"),
      list(id = "k", label = "K"),
      list(id = "bb", label = "BB"),
      list(id = "hbp", label = "HBP"),
      list(id = "hr", label = "HR"),
      list(id = "fly", label = "FLY%"),
      list(id = "ground", label = "GB%")
    )) {
      stat_val <- notes[[paste0("stats_", stat$id)]] %||% "-"
      cat('<div class="stat-cell">')
      cat(sprintf('<div class="stat-label">%s</div>', stat$label))
      cat(sprintf('<div class="stat-value">%s</div>', stat_val))
      cat('</div>')
    }
    cat('</div>')

    # Notes
    cat('<div class="notes-box">')
    cat('<div class="notes-label">NOTES</div>')
    cat(sprintf('<div>%s</div>', notes$notes_main %||% ""))
    cat('</div>')

    # Action
    cat('<div class="notes-box">')
    cat('<div class="notes-label">ACTION</div>')
    cat(sprintf('<div>%s</div>', notes$notes_action %||% ""))
    cat('</div>')

    cat('</div>')  # End stats-notes-row

    cat('</div>')  # End batter-section
  }

} else {
  cat('<div style="text-align: center; padding: 50px; color: #888;">')
  cat('<h4>No batters loaded</h4>')
  cat('</div>')
}
```

<div class="footer">
Report generated `r Sys.Date()` | Cal Poly Baseball | Print (Ctrl/Cmd + P) to save as PDF
</div>
