---
title: ""
output:
  html_document:
    theme: null
    self_contained: true
    css: null
params:
  pitcher: "Unknown Pitcher"
  team: "Unknown Team"
  dates: !r c(Sys.Date() - 30, Sys.Date())
  split: "Both"
  arsenal: NULL
  pitch_data: NULL
  pitcher_image: NULL
  notes: !r list(gameplan = "", attack = "", first_pitch = "", hitter_adv = "", two_k = "")
  pitch_descriptions: NULL
  risp_images: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center")
library(tidyverse)
library(kableExtra)
library(viridisLite)

# Helper function to generate heatmap
generate_heatmap_pdf <- function(df, pitch_type = NULL, title = "") {
  plot_data <- if (!is.null(pitch_type) && "pitch_type_display" %in% names(df)) {
    df |> filter(pitch_type_display == pitch_type)
  } else if (!is.null(pitch_type)) {
    df |> filter(taggedpitchtype == pitch_type)
  } else {
    df
  }

  plot_data <- plot_data |> filter(!is.na(platelocside), !is.na(platelocheight))

  if (nrow(plot_data) < 3) {
    return(
      ggplot() +
        annotate("text", x = 0, y = 2.5, label = "N/A", size = 4) +
        theme_void() +
        labs(title = title)
    )
  }

  cols <- viridisLite::turbo(256)
  cols[1] <- "white"

  ggplot(plot_data, aes(x = platelocside, y = platelocheight)) +
    stat_density_2d(
      aes(fill = after_stat(ndensity)),
      geom = "raster",
      contour = FALSE,
      h = c(0.55, 0.55),
      n = 100
    ) +
    scale_fill_gradientn(colors = cols, guide = "none") +
    annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5,
             fill = NA, color = "black", linewidth = 0.8) +
    annotate("segment", x = -0.85, xend = 0.85, y = 0, yend = 0, color = "black") +
    annotate("segment", x = -0.85, xend = -0.85, y = 0, yend = -0.15, color = "black") +
    annotate("segment", x = 0.85, xend = 0.85, y = 0, yend = -0.15, color = "black") +
    annotate("segment", x = -0.85, xend = 0, y = -0.15, yend = -0.3, color = "black") +
    annotate("segment", x = 0.85, xend = 0, y = -0.15, yend = -0.3, color = "black") +
    coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
    labs(title = title) +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5, size = 9, face = "bold"))
}

# Get pitch usage for a filtered dataset
get_pitch_usage <- function(df) {
  df |>
    count(pitch_type_display) |>
    mutate(pct = round(n / sum(n) * 100, 0)) |>
    arrange(desc(n))
}

# Calculate zone percentage
calculate_zone_pct_report <- function(df) {
  if (nrow(df) == 0) return(NA_real_)
  zone_left <- -0.83
  zone_right <- 0.83
  zone_bottom <- 1.5
  zone_top <- 3.5
  in_zone <- df |>
    filter(
      platelocside >= zone_left,
      platelocside <= zone_right,
      platelocheight >= zone_bottom,
      platelocheight <= zone_top
    ) |>
    nrow()
  round(in_zone / nrow(df) * 100, 0)
}

# Generate SLG heatmap - shows density of hits
generate_slg_heatmap_report <- function(df, title = "SLG by Zone") {
  hit_df <- df |>
    filter(pitchcall == "InPlay" & !is.na(platelocside) & !is.na(platelocheight)) |>
    filter(playresult %in% c("Single", "SIngle", "Double", "Triple", "triple", "HomeRun", "Homerun"))
  if (nrow(hit_df) < 3) {
    return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 4) +
           theme_void() + labs(title = title))
  }
  cols <- viridisLite::turbo(256)
  cols[1] <- "white"
  ggplot(hit_df, aes(x = platelocside, y = platelocheight)) +
    stat_density_2d(aes(fill = after_stat(ndensity)), geom = "raster", contour = FALSE, h = c(0.55, 0.55), n = 80) +
    scale_fill_gradientn(colors = cols, guide = "none") +
    annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5,
             fill = NA, color = "black", linewidth = 0.8) +
    annotate("segment", x = -0.85, xend = 0.85, y = 0, yend = 0, color = "black") +
    annotate("segment", x = -0.85, xend = -0.85, y = 0, yend = -0.15, color = "black") +
    annotate("segment", x = 0.85, xend = 0.85, y = 0, yend = -0.15, color = "black") +
    annotate("segment", x = -0.85, xend = 0, y = -0.15, yend = -0.3, color = "black") +
    annotate("segment", x = 0.85, xend = 0, y = -0.15, yend = -0.3, color = "black") +
    coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
    labs(title = title) +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5, size = 9, face = "bold"))
}

# Generate Whiff Heatmap - shows density of swinging strikes (same as SLG)
generate_whiff_heatmap_report <- function(df, title = "Whiffs") {
  whiff_df <- df |>
    filter(pitchcall == "StrikeSwinging" & !is.na(platelocside) & !is.na(platelocheight))
  if (nrow(whiff_df) < 3) {
    return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 4) +
           theme_void() + labs(title = title))
  }
  cols <- viridisLite::turbo(256)
  cols[1] <- "white"
  ggplot(whiff_df, aes(x = platelocside, y = platelocheight)) +
    stat_density_2d(aes(fill = after_stat(ndensity)), geom = "raster", contour = FALSE, h = c(0.55, 0.55), n = 80) +
    scale_fill_gradientn(colors = cols, guide = "none") +
    annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5,
             fill = NA, color = "black", linewidth = 0.8) +
    annotate("segment", x = -0.85, xend = 0.85, y = 0, yend = 0, color = "black") +
    annotate("segment", x = -0.85, xend = -0.85, y = 0, yend = -0.15, color = "black") +
    annotate("segment", x = 0.85, xend = 0.85, y = 0, yend = -0.15, color = "black") +
    annotate("segment", x = -0.85, xend = 0, y = -0.15, yend = -0.3, color = "black") +
    annotate("segment", x = 0.85, xend = 0, y = -0.15, yend = -0.3, color = "black") +
    coord_fixed(xlim = c(-2, 2), ylim = c(-0.5, 4.5), expand = FALSE) +
    labs(title = title) +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5, size = 9, face = "bold"))
}

# Calculate pitcher info
pitcher_info <- if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data
  list(
    extension = sprintf("%.1f ft", mean(df$extension, na.rm = TRUE)),
    rel_height = sprintf("%.1f ft", mean(df$relheight, na.rm = TRUE)),
    throws = if(mean(df$relside, na.rm = TRUE) > 0) "RHP" else "LHP"
  )
} else {
  list(extension = "N/A", rel_height = "N/A", throws = "N/A")
}
```

<style>
/* Base styles */
body {
  font-family: Arial, sans-serif;
  font-size: 11px;
  margin: 0;
  padding: 10px;
  max-width: 100%;
}

/* Print-specific styles */
@media print {
  @page {
    size: letter;
    margin: 0.4in;
  }

  body {
    -webkit-print-color-adjust: exact;
    print-color-adjust: exact;
    font-size: 10px;
    padding: 0;
    margin: 0;
  }

  /* Prevent page breaks inside these elements */
  .header-box,
  .arsenal-section,
  .heatmap-section {
    page-break-inside: avoid;
  }

  /* Force page break before page 2 content */
  .page-break-before {
    page-break-before: always;
  }

  /* Ensure sections stay together */
  .section-header {
    page-break-after: avoid;
  }

  .heatmap-row {
    page-break-inside: avoid;
  }

  /* Hide hover effects in print */
  .arsenal-table tr:hover {
    background: inherit;
  }

  /* Compact spacing for print */
  .section-header {
    margin: 8px 0 6px 0;
    padding: 5px 10px;
  }

  .heatmap-row {
    margin-bottom: 6px;
  }

  .notes-box {
    min-height: 80px;
    padding: 5px;
    font-size: 9px;
  }

  /* Hide footer or make it subtle */
  .footer {
    margin-top: 10px;
    padding-top: 5px;
  }

  /* Ensure images don't overflow */
  img {
    max-width: 100%;
    height: auto;
  }
}

.header-box {
  background: #1a365d;
  color: white;
  padding: 10px 15px;
  margin-bottom: 10px;
  border-radius: 4px;
}
.header-box h1 {
  margin: 0;
  font-size: 18px;
}
.header-box .subtitle {
  font-size: 11px;
  opacity: 0.9;
}
.arsenal-section {
  margin-bottom: 10px;
}
.arsenal-table {
  width: 100%;
  border-collapse: collapse;
  font-size: 13px;
  margin-bottom: 10px;
}
.arsenal-table th {
  background: #2d3748;
  color: white;
  padding: 8px 6px;
  text-align: center;
  font-weight: 600;
  font-size: 12px;
}
.arsenal-table td {
  padding: 6px;
  text-align: center;
  border-bottom: 1px solid #e2e8f0;
  font-size: 12px;
}
.arsenal-table tr:nth-child(even) {
  background: #f7fafc;
}
.arsenal-table tr:hover {
  background: #edf2f7;
}
.section-header {
  background: #4a5568;
  color: white;
  padding: 6px 12px;
  margin: 10px 0 6px 0;
  font-weight: 600;
  font-size: 11px;
  border-radius: 3px;
}
.heatmap-section {
  margin-bottom: 8px;
}
.heatmap-row {
  display: flex;
  gap: 8px;
  margin-bottom: 6px;
  align-items: flex-start;
}
.notes-box {
  background: #fffbeb;
  border: 1px solid #f6e05e;
  border-radius: 4px;
  padding: 6px;
  min-width: 130px;
  max-width: 140px;
  font-size: 9px;
  min-height: 100px;
}
.notes-box strong {
  display: block;
  margin-bottom: 4px;
  color: #744210;
  font-size: 10px;
}
.heatmap-container {
  text-align: center;
}
.footer {
  margin-top: 15px;
  padding-top: 8px;
  border-top: 1px solid #e2e8f0;
  font-size: 8px;
  color: #718096;
  text-align: center;
}

/* Two-page layout helper */
.page-1 {
  min-height: auto;
}
.page-2 {
  min-height: auto;
}
</style>

```{r header-image, results='asis', echo=FALSE}
cat('<div class="header-box">')
cat(sprintf('<h1 style="margin: 0;">%s | %s</h1>', params$pitcher, params$team))
split_text <- if(params$split == "Both") "All Batters" else if(params$split == "Left") "vs LHH" else "vs RHH"
cat(sprintf('<div class="subtitle">%s | Extension: %s | Release Height: %s | Split: %s</div>',
            pitcher_info$throws, pitcher_info$extension, pitcher_info$rel_height, split_text))
cat('</div>')
```

<!-- PAGE 1: Arsenal + Overall + First Pitch -->
<div class="page-1">

<div class="arsenal-section">
<h4 style="margin: 0 0 8px 0; color: #2d3748; font-size: 13px; border-bottom: 2px solid #2d3748; padding-bottom: 4px;">PITCH ARSENAL</h4>
<table style="width: 100%; border-collapse: collapse; table-layout: fixed;">
<tr>
<td style="vertical-align: top; padding-right: 15px;">
```{r arsenal-table, results='asis', echo=FALSE}
# Output arsenal table
if (!is.null(params$arsenal) && nrow(params$arsenal) > 0) {
  arsenal_display <- params$arsenal |>
    mutate(
      usage = paste0(usage, "%"),
      zone_pct_styled = ifelse(zone_pct < 40,
        paste0('<span style="color: darkred; font-weight: bold; background: rgba(255,200,200,0.8); padding: 2px 4px;">', zone_pct, '%</span>'),
        paste0(zone_pct, '%'))
    ) |>
    select(pitch_type, usage, velo, zone_pct_styled, ivb, hb)

  print(kable(arsenal_display,
        col.names = c("Pitch Type", "Usage", "Velo", "Zone%", "IVB", "HB"),
        align = "c",
        format = "html",
        escape = FALSE,
        table.attr = 'class="arsenal-table"') |>
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = TRUE))
} else {
  cat("<p>No arsenal data available.</p>")
}
```

<table style="width: 100%; border-collapse: collapse; height: 280px; margin-top: 8px;">
<tr>
<td style="width: 160px; vertical-align: top; padding-right: 10px;">
<div style="display: flex; flex-direction: column; gap: 6px;">

```{r pitcher-image, results='asis', echo=FALSE}
if (!is.null(params$pitcher_image) && params$pitcher_image != "") {
  cat(sprintf('<img src="%s" style="width: 150px; height: 200px; object-fit: cover; border-radius: 6px; border: 2px solid #1a365d;" />', params$pitcher_image))
} else {
  cat('<div style="width: 150px; height: 200px; background: #f0f0f0; border-radius: 6px; display: flex; align-items: center; justify-content: center;"><span style="color: #888; font-size: 10px;">No image</span></div>')
}
```

<div style="background: #e2e8f0; border-radius: 4px; padding: 6px; text-align: center;">
<div style="font-size: 9px; color: #4a5568; margin-bottom: 2px;">EXTENSION</div>
<div style="font-size: 14px; font-weight: bold; color: #1a365d;">`r pitcher_info$extension`</div>
</div>
<div style="background: #e2e8f0; border-radius: 4px; padding: 6px; text-align: center;">
<div style="font-size: 9px; color: #4a5568; margin-bottom: 2px;">REL HEIGHT</div>
<div style="font-size: 14px; font-weight: bold; color: #1a365d;">`r pitcher_info$rel_height`</div>
</div>
</div>
</td>
<td style="vertical-align: top;">
<div style="background: #fffbeb; border: 1px solid #f6e05e; border-radius: 4px; padding: 10px; height: 100%; min-height: 260px; box-sizing: border-box;">
<strong style="color: #744210; font-size: 12px; display: block; margin-bottom: 6px;">GAMEPLAN NOTES</strong>
<p style="margin: 0; font-size: 11px; white-space: pre-wrap; line-height: 1.4;">`r if(!is.null(params$notes$gameplan) && params$notes$gameplan != "") params$notes$gameplan else "No gameplan notes"`</p>
</div>
</td>
</tr>
</table>
</td>
<td style="width: 160px; vertical-align: top;">
```{r slg-heatmap, fig.height=1.6, fig.width=1.6, out.width="100%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  generate_slg_heatmap_report(params$pitch_data, "Hits")
}
```
```{r whiff-heatmap, fig.height=1.6, fig.width=1.6, out.width="100%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  generate_whiff_heatmap_report(params$pitch_data, "Whiffs")
}
```
<div style="background: #f7fafc; border: 1px solid #e2e8f0; border-radius: 4px; padding: 6px; text-align: center; flex: 1; display: flex; flex-direction: column; justify-content: center;">
<strong style="font-size: 10px;">Zone %</strong>
```{r zone-pct, results='asis'}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  zone_pct <- calculate_zone_pct_report(params$pitch_data)
  zone_color <- if (!is.na(zone_pct) && zone_pct < 40) "darkred" else "#2d3748"
  cat(sprintf('<p style="font-size: 22px; font-weight: bold; color: %s; margin: 4px 0;">%s%%</p>', zone_color, zone_pct))
} else {
  cat('<p style="font-size: 22px; font-weight: bold; margin: 4px 0;">N/A</p>')
}
```
</div>
</td>
</tr>
</table>
</div>

<div class="heatmap-section">
<div class="section-header">OVERALL ATTACK</div>
<div class="heatmap-row">
<div class="notes-box">
<strong>Notes:</strong>
`r if(!is.null(params$notes$attack) && params$notes$attack != "") params$notes$attack else "No notes"`
</div>
```{r overall-heatmaps, fig.height=1.8, fig.width=10, out.width="78%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data
  usage <- get_pitch_usage(df)
  top_pitches <- head(usage, 6)  # Max 6 per row for layout
  if (nrow(top_pitches) > 0) {
    plots <- lapply(seq_len(nrow(top_pitches)), function(i) {
      pt <- top_pitches$pitch_type_display[i]
      pct <- top_pitches$pct[i]
      generate_heatmap_pdf(df, pt, paste0(pt, " (", pct, "%)"))
    })
    gridExtra::grid.arrange(grobs = plots, nrow = 1)
  }
}
```
</div>
</div>

<div class="heatmap-section">
<div class="section-header">FIRST PITCH (0-0)</div>
<div class="heatmap-row">
<div class="notes-box">
<strong>Notes:</strong>
`r if(!is.null(params$notes$first_pitch) && params$notes$first_pitch != "") params$notes$first_pitch else "No notes"`
</div>
```{r first-pitch-heatmaps, fig.height=1.8, fig.width=10, out.width="78%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data |> filter(balls == 0 & strikes == 0)
  if (nrow(df) >= 3) {
    usage <- get_pitch_usage(df)
    top_pitches <- head(usage, 6)  # Max 6 per row for layout
    if (nrow(top_pitches) > 0) {
      plots <- lapply(seq_len(nrow(top_pitches)), function(i) {
        pt <- top_pitches$pitch_type_display[i]
        pct <- top_pitches$pct[i]
        generate_heatmap_pdf(df, pt, paste0(pt, " (", pct, "%)"))
      })
      gridExtra::grid.arrange(grobs = plots, nrow = 1)
    }
  } else {
    cat("Insufficient first pitch data")
  }
}
```
</div>
</div>

</div>

<!-- PAGE 2: Hitter Advantage + 2K -->
<div class="page-2 page-break-before">

<div class="heatmap-section">
<div class="section-header">HITTER ADVANTAGE (1-0, 2-0, 2-1, 3-0, 3-1)</div>
<div class="heatmap-row">
<div class="notes-box">
<strong>Notes:</strong>
`r if(!is.null(params$notes$hitter_adv) && params$notes$hitter_adv != "") params$notes$hitter_adv else "No notes"`
</div>
```{r hitter-adv-heatmaps, fig.height=1.8, fig.width=10, out.width="78%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data |>
    filter(
      (balls == 1 & strikes == 0) |
      (balls == 2 & strikes %in% c(0, 1)) |
      (balls == 3 & strikes %in% c(0, 1))
    )
  if (nrow(df) >= 3) {
    usage <- get_pitch_usage(df)
    top_pitches <- head(usage, 6)  # Max 6 per row for layout
    if (nrow(top_pitches) > 0) {
      plots <- lapply(seq_len(nrow(top_pitches)), function(i) {
        pt <- top_pitches$pitch_type_display[i]
        pct <- top_pitches$pct[i]
        generate_heatmap_pdf(df, pt, paste0(pt, " (", pct, "%)"))
      })
      gridExtra::grid.arrange(grobs = plots, nrow = 1)
    }
  } else {
    cat("Insufficient hitter advantage data")
  }
}
```
</div>
</div>

<div class="heatmap-section">
<div class="section-header">TWO STRIKES (2K)</div>
<div class="heatmap-row">
<div class="notes-box">
<strong>Notes:</strong>
`r if(!is.null(params$notes$two_k) && params$notes$two_k != "") params$notes$two_k else "No notes"`
</div>
```{r 2k-heatmaps, fig.height=1.8, fig.width=10, out.width="78%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data |> filter(strikes == 2)
  if (nrow(df) >= 3) {
    usage <- get_pitch_usage(df)
    top_pitches <- head(usage, 6)  # Max 6 per row for layout
    if (nrow(top_pitches) > 0) {
      plots <- lapply(seq_len(nrow(top_pitches)), function(i) {
        pt <- top_pitches$pitch_type_display[i]
        pct <- top_pitches$pct[i]
        generate_heatmap_pdf(df, pt, paste0(pt, " (", pct, "%)"))
      })
      gridExtra::grid.arrange(grobs = plots, nrow = 1)
    }
  } else {
    cat("Insufficient 2K data")
  }
}
```
</div>
</div>

<div class="heatmap-section">
<div class="section-header">RISP (RUNNERS IN SCORING POSITION)</div>
<div class="heatmap-row">
<div class="notes-box">
<strong>Notes:</strong>
Manual heatmaps - no baserunner data available
</div>
```{r risp-images, results='asis', echo=FALSE}
if (!is.null(params$risp_images) && length(params$risp_images) > 0) {
  cat('<div style="display: flex; gap: 10px; flex-wrap: wrap;">')
  for (pt in names(params$risp_images)) {
    url <- params$risp_images[[pt]]
    if (!is.null(url) && url != "") {
      cat(sprintf('<div class="heatmap-container" style="text-align: center;"><img src="%s" style="max-width:130px; max-height:140px; border-radius: 4px;"/><div style="font-size: 9px; font-weight: bold; margin-top: 3px;">%s</div></div>', url, pt))
    }
  }
  cat('</div>')
} else {
  cat('<div style="color: #888; font-style: italic;">No RISP images uploaded</div>')
}
```
</div>
</div>

```{r pitch-descriptions, results='asis', echo=FALSE}
if (!is.null(params$pitch_descriptions) && length(params$pitch_descriptions) > 0) {
  cat('<div class="heatmap-section">')
  cat('<div class="section-header">PITCH DESCRIPTIONS</div>')
  cat('<div style="background: #f7fafc; border: 1px solid #e2e8f0; border-radius: 4px; padding: 10px;">')
  cat('<table style="width: 100%; font-size: 11px;">')
  for (pt in names(params$pitch_descriptions)) {
    desc <- params$pitch_descriptions[[pt]]
    if (!is.null(desc) && desc != "") {
      cat(sprintf('<tr><td style="font-weight: bold; width: 120px; padding: 3px 8px;">%s:</td><td style="padding: 3px 8px;">%s</td></tr>', pt, desc))
    }
  }
  cat('</table>')
  cat('</div>')
  cat('</div>')
}
```

</div>

<div class="footer">
Report generated on `r Sys.Date()` | Cal Poly Baseball Scouting System | Print this page (Ctrl/Cmd + P) to save as PDF
</div>
