---
title: ""
output:
  html_document:
    theme: null
    self_contained: true
    css: null
params:
  pitcher: "Unknown Pitcher"
  team: "Unknown Team"
  dates: !r c(Sys.Date() - 30, Sys.Date())
  split: "Both"
  arsenal: NULL
  pitch_data: NULL
  pitcher_image: NULL
  notes: !r list(gameplan = "", attack = "", first_pitch = "", hitter_adv = "", two_k = "", risp = "")
  pitch_descriptions: NULL
  risp_images: NULL
  risp_usages: NULL
  pitcher_stats: !r list(ip = "", era = "", k = "", bb = "", baa_lhh = "", baa_rhh = "")
  grade: ""
  out_pitch: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center")
library(tidyverse)
library(kableExtra)
library(viridisLite)

# Pitch type color scheme
get_pitch_color <- function(pitch_type) {
  pt_upper <- toupper(pitch_type)
  colors <- list(
    "FASTBALL" = list(bg = "#fee2e2", text = "#dc2626"),
    "FB" = list(bg = "#fee2e2", text = "#dc2626"),
    "FOUR-SEAM" = list(bg = "#fee2e2", text = "#dc2626"),
    "CHANGEUP" = list(bg = "#dbeafe", text = "#2563eb"),
    "CH" = list(bg = "#dbeafe", text = "#2563eb"),
    "SLIDER" = list(bg = "#dcfce7", text = "#16a34a"),
    "SL" = list(bg = "#dcfce7", text = "#16a34a"),
    "CURVEBALL" = list(bg = "#ffedd5", text = "#ea580c"),
    "CB" = list(bg = "#ffedd5", text = "#ea580c"),
    "CU" = list(bg = "#ffedd5", text = "#ea580c"),
    "CUTTER" = list(bg = "#f3e8ff", text = "#9333ea"),
    "FC" = list(bg = "#f3e8ff", text = "#9333ea"),
    "SINKER" = list(bg = "#fef3c7", text = "#d97706"),
    "SI" = list(bg = "#fef3c7", text = "#d97706"),
    "SPLITTER" = list(bg = "#ccfbf1", text = "#0d9488"),
    "FS" = list(bg = "#ccfbf1", text = "#0d9488"),
    "SWEEPER" = list(bg = "#e0e7ff", text = "#4f46e5")
  )
  if (pt_upper %in% names(colors)) colors[[pt_upper]] else list(bg = "#f3f4f6", text = "#374151")
}

get_mech_color <- function(val) {
  if (is.na(val) || is.nan(val) || !is.finite(val)) {
    return(list(bg = "#e2e8f0", text = "#1a1a1a"))
  }
  if      (val >= 6.75)  list(bg = "#39FF14", text = "#1a1a1a")  # neon green
  else if (val >= 6.5)   list(bg = "#16a34a", text = "#ffffff")   # darker green
  else if (val >= 6.25)  list(bg = "#bbf7d0", text = "#14532d")   # light soft green
  else if (val >= 5.833) list(bg = "#e2e8f0", text = "#1a1a1a")   # neutral gray
  else if (val >= 5.583) list(bg = "#fecaca", text = "#991b1b")   # light pink/red
  else if (val >= 5.333) list(bg = "#dc2626", text = "#ffffff")   # darker red
  else                   list(bg = "#ff0000", text = "#ffffff")   # bright red
}

# Nadaraya-Watson 2D kernel regression
nadaraya_watson_2d <- function(x, y, values, bw = 0.55, n = 60,
                                xlim = c(-2, 2), ylim = c(-0.5, 4.5)) {
  x_grid <- seq(xlim[1], xlim[2], length.out = n)
  y_grid <- seq(ylim[1], ylim[2], length.out = n)
  grid <- expand.grid(gx = x_grid, gy = y_grid)
  dx_mat <- outer(grid$gx, x, FUN = "-")
  dy_mat <- outer(grid$gy, y, FUN = "-")
  K <- exp(-(dx_mat^2 + dy_mat^2) / (2 * bw^2))
  denom <- rowSums(K)
  grid$value <- ifelse(denom < 1e-6, NA_real_, as.vector(K %*% values) / denom)
  grid
}

# Helper function to generate per-pitch location heatmap (overall attack rows)
generate_heatmap_pdf <- function(df, pitch_type = NULL, title = "", pct = NULL) {
  plot_data <- if (!is.null(pitch_type) && "pitch_type_display" %in% names(df)) {
    df |> filter(pitch_type_display == pitch_type)
  } else if (!is.null(pitch_type)) {
    df |> filter(taggedpitchtype == pitch_type)
  } else {
    df
  }

  plot_data <- plot_data |> filter(!is.na(platelocside), !is.na(platelocheight))

  if (nrow(plot_data) < 3) {
    return(
      ggplot() +
        annotate("text", x = 0, y = 2.5, label = "N/A", size = 3) +
        theme_void() +
        labs(title = title) +
        theme(plot.title = element_text(hjust = 0.5, size = 7, face = "bold"))
    )
  }

  cols <- viridisLite::turbo(256)
  cols[1] <- "white"

  ggplot(plot_data, aes(x = platelocside, y = platelocheight)) +
    stat_density_2d(
      aes(fill = after_stat(ndensity)),
      geom = "raster",
      contour = FALSE,
      h = c(0.55, 0.55),
      n = 80
    ) +
    scale_fill_gradientn(colors = cols, guide = "none") +
    annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5,
             fill = NA, color = "black", linewidth = 0.6) +
    annotate("segment", x = -0.85, xend = 0.85, y = 0, yend = 0, color = "black", linewidth = 0.4) +
    annotate("segment", x = -0.85, xend = -0.85, y = 0, yend = -0.15, color = "black", linewidth = 0.4) +
    annotate("segment", x = 0.85, xend = 0.85, y = 0, yend = -0.15, color = "black", linewidth = 0.4) +
    annotate("segment", x = -0.85, xend = 0, y = -0.15, yend = -0.3, color = "black", linewidth = 0.4) +
    annotate("segment", x = 0.85, xend = 0, y = -0.15, yend = -0.3, color = "black", linewidth = 0.4) +
    coord_fixed(xlim = c(-2, 2), ylim = c(0.75, 4.25), expand = FALSE) +
    labs(title = title) +
    theme_void() +
    theme(
      plot.title = element_text(hjust = 0.5, size = 8, face = "bold", color = "#1e3a5f"),
      plot.background = element_rect(fill = "white", color = NA),
      plot.margin = margin(2, 2, 2, 2)
    )
}

# Get pitch usage for a filtered dataset
get_pitch_usage <- function(df) {
  df |>
    count(pitch_type_display) |>
    mutate(pct = round(n / sum(n) * 100, 0)) |>
    arrange(desc(n))
}

# Colored header grob for a pitch type (matches RISP badge style)
make_header_grob <- function(pt, pct = NULL) {
  colors <- get_pitch_color(pt)
  label <- if (!is.null(pct) && !is.na(pct)) paste0(pt, " (", pct, "%)") else paste0(pt, " (-)")
  grid::grobTree(
    grid::rectGrob(gp = grid::gpar(fill = colors$bg, col = NA)),
    grid::textGrob(label, gp = grid::gpar(col = colors$text, fontface = "bold", fontsize = 9))
  )
}

# Blank placeholder grob for empty pitch slots (keeps columns aligned)
make_blank_grob <- function() {
  grid::rectGrob(gp = grid::gpar(col = NA, fill = NA))
}

# Reorder situation usage to match the canonical arsenal order (fastball first, then overall usage)
order_by_canonical <- function(df, canonical_pts, max_pitches = 6) {
  usage <- df |>
    count(pitch_type_display) |>
    mutate(pct = round(n / sum(n) * 100, 0))
  data.frame(pitch_type_display = canonical_pts, stringsAsFactors = FALSE) |>
    dplyr::left_join(usage, by = "pitch_type_display") |>
    dplyr::filter(!is.na(n)) |>
    head(max_pitches)
}

# Calculate zone percentage
calculate_zone_pct_report <- function(df) {
  if (nrow(df) == 0) return(NA_real_)
  in_zone <- df |>
    filter(platelocside >= -0.83, platelocside <= 0.83,
           platelocheight >= 1.5, platelocheight <= 3.5) |>
    nrow()
  round(in_zone / nrow(df) * 100, 0)
}

# Generate SLG heatmap (NW regression, compact)
generate_slg_heatmap_report <- function(df, title = "Damage") {
  valid_df <- df |> filter(!is.na(platelocside), !is.na(platelocheight))
  if (nrow(valid_df) < 5) {
    return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 3) +
           theme_void() + labs(title = title) +
           theme(plot.title = element_text(hjust = 0.5, size = 8, face = "bold", color = "#991b1b")))
  }
  slg_weights <- dplyr::case_when(
    valid_df$playresult %in% c("HomeRun", "Homerun") ~ 4,
    valid_df$playresult %in% c("Triple", "triple") ~ 3,
    valid_df$playresult == "Double" ~ 2,
    valid_df$playresult %in% c("Single", "SIngle") ~ 1,
    TRUE ~ 0
  )
  grid_df <- nadaraya_watson_2d(valid_df$platelocside, valid_df$platelocheight, slg_weights, bw = 0.30, n = 80)
  cols <- viridisLite::turbo(256)
  cols[1] <- "white"
  ggplot() +
    geom_raster(data = grid_df, aes(x = gx, y = gy, fill = value)) +
    scale_fill_gradientn(colors = cols, na.value = "white", guide = "none") +
    geom_point(data = valid_df, aes(x = platelocside, y = platelocheight),
               color = "white", size = 0.25, alpha = 0.35, inherit.aes = FALSE) +
    annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5,
             fill = NA, color = "black", linewidth = 0.5) +
    annotate("segment", x = -0.85, xend = 0.85, y = 0, yend = 0, color = "black", linewidth = 0.4) +
    annotate("segment", x = -0.85, xend = -0.85, y = 0, yend = -0.15, color = "black", linewidth = 0.4) +
    annotate("segment", x = 0.85, xend = 0.85, y = 0, yend = -0.15, color = "black", linewidth = 0.4) +
    annotate("segment", x = -0.85, xend = 0, y = -0.15, yend = -0.3, color = "black", linewidth = 0.4) +
    annotate("segment", x = 0.85, xend = 0, y = -0.15, yend = -0.3, color = "black", linewidth = 0.4) +
    coord_fixed(xlim = c(-2, 2), ylim = c(0.75, 4.25), expand = FALSE) +
    labs(title = title) +
    theme_void() +
    theme(
      plot.title = element_text(hjust = 0.5, size = 8, face = "bold", color = "#991b1b"),
      plot.margin = margin(0, 0, 0, 0)
    )
}

# Generate Whiff heatmap (NW regression, compact)
generate_whiff_heatmap_report <- function(df, title = "Swing & Miss") {
  valid_df <- df |> filter(!is.na(platelocside), !is.na(platelocheight))
  if (nrow(valid_df) < 5) {
    return(ggplot() + annotate("text", x = 0, y = 2.5, label = "N/A", size = 3) +
           theme_void() + labs(title = title) +
           theme(plot.title = element_text(hjust = 0.5, size = 8, face = "bold", color = "#1e3a5f")))
  }
  is_whiff <- as.numeric(valid_df$pitchcall == "StrikeSwinging")
  grid_df <- nadaraya_watson_2d(valid_df$platelocside, valid_df$platelocheight, is_whiff, bw = 0.30, n = 80)
  cols <- viridisLite::turbo(256)
  cols[1] <- "white"
  ggplot() +
    geom_raster(data = grid_df, aes(x = gx, y = gy, fill = value)) +
    scale_fill_gradientn(colors = cols, na.value = "white", guide = "none") +
    geom_point(data = valid_df, aes(x = platelocside, y = platelocheight),
               color = "white", size = 0.25, alpha = 0.35, inherit.aes = FALSE) +
    annotate("rect", xmin = -0.83, xmax = 0.83, ymin = 1.5, ymax = 3.5,
             fill = NA, color = "black", linewidth = 0.5) +
    annotate("segment", x = -0.85, xend = 0.85, y = 0, yend = 0, color = "black", linewidth = 0.4) +
    annotate("segment", x = -0.85, xend = -0.85, y = 0, yend = -0.15, color = "black", linewidth = 0.4) +
    annotate("segment", x = 0.85, xend = 0.85, y = 0, yend = -0.15, color = "black", linewidth = 0.4) +
    annotate("segment", x = -0.85, xend = 0, y = -0.15, yend = -0.3, color = "black", linewidth = 0.4) +
    annotate("segment", x = 0.85, xend = 0, y = -0.15, yend = -0.3, color = "black", linewidth = 0.4) +
    coord_fixed(xlim = c(-2, 2), ylim = c(0.75, 4.25), expand = FALSE) +
    labs(title = title) +
    theme_void() +
    theme(
      plot.title = element_text(hjust = 0.5, size = 8, face = "bold", color = "#1e3a5f"),
      plot.margin = margin(0, 0, 0, 0)
    )
}

# Helper: format decimal feet as feet-and-inches (e.g. 5.5 -> "5' 6\"")
format_feet_inches <- function(ft) {
  if (is.na(ft) || !is.finite(ft)) return("N/A")
  total_inches <- round(ft * 12)
  sprintf("%d' %d\"", total_inches %/% 12L, total_inches %% 12L)
}

# Calculate pitcher info — extension and release height use fastballs/sinkers only
pitcher_info <- if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data
  fb_types <- c("Fastball", "FourSeamFastBall", "TwoSeamFastBall", "OneSeamFastBall", "Sinker")
  fb_df <- df |> filter(pitch_type_display %in% fb_types |
                          grepl("fastball|sinker", pitch_type_display, ignore.case = TRUE))
  mech_df <- if (nrow(fb_df) >= 3) fb_df else df  # fall back to all pitches if no FB data
  list(
    extension  = format_feet_inches(mean(mech_df$extension, na.rm = TRUE)),
    rel_height = format_feet_inches(mean(mech_df$relheight, na.rm = TRUE)),
    throws     = if (mean(df$relside, na.rm = TRUE) > 0) "RHP" else "LHP"
  )
} else {
  list(extension = "N/A", rel_height = "N/A", throws = "N/A")
}
```

<style>
/* Compact single-page layout */
body {
  font-family: Arial, sans-serif;
  font-size: 11px;
  margin: 0;
  padding: 5px;
  max-width: 100%;
}

@media print {
  @page { size: letter; margin: 0.25in; }
  body {
    -webkit-print-color-adjust: exact;
    print-color-adjust: exact;
    font-size: 10px;
    padding: 0;
    margin: 0;
  }
  .no-break { page-break-inside: avoid; }
}

.header-box {
  background: #1a365d;
  color: white;
  padding: 6px 10px;
  margin-bottom: 5px;
  border-radius: 3px;
}
.header-box h1 { margin: 0; font-size: 16px; }
.header-box .subtitle { font-size: 11px; opacity: 0.9; }

.arsenal-table {
  width: 100%;
  border-collapse: collapse;
  font-size: 11px;
}
.arsenal-table th {
  background: #2d3748;
  color: white;
  padding: 4px 5px;
  text-align: center;
  font-size: 10px;
}
.arsenal-table td {
  padding: 3px 5px;
  text-align: center;
  border-bottom: 1px solid #e2e8f0;
  font-size: 11px;
}
.arsenal-table tr.footer-row td {
  background: #edf2f7;
  font-weight: bold;
  font-size: 10px;
  border-top: 2px solid #4a5568;
}

.section-header {
  background: #4a5568;
  color: white;
  padding: 3px 8px;
  margin: 3px 0 2px 0;
  font-weight: 600;
  font-size: 11px;
  border-radius: 2px;
}

.heatmap-row {
  display: flex;
  gap: 4px;
  margin-bottom: 2px;
  align-items: flex-start;
}

.notes-box {
  background: #fffbeb;
  border: 1px solid #f6e05e;
  border-radius: 3px;
  padding: 3px 5px;
  min-width: 90px;
  max-width: 100px;
  font-size: 9px;
  min-height: 45px;
}
.notes-box strong {
  display: block;
  margin-bottom: 2px;
  color: #744210;
  font-size: 10px;
}

.stat-box {
  background: #e2e8f0;
  border-radius: 3px;
  padding: 4px 6px;
  text-align: center;
  margin-bottom: 3px;
}
.stat-label { font-size: 9px; color: #4a5568; }
.stat-value { font-size: 13px; font-weight: bold; color: #1a365d; }

.grade-box {
  background: #fffbeb;
  border: 1px solid #f6e05e;
  border-radius: 3px;
  padding: 4px 6px;
  text-align: center;
  margin-bottom: 3px;
}
.grade-label { font-size: 9px; color: #744210; }
.grade-value { font-size: 13px; font-weight: bold; color: #744210; }

.heatmap-label {
  background: #2d3748;
  color: white;
  padding: 3px 4px;
  font-size: 10px;
  font-weight: bold;
  text-align: center;
  border-radius: 2px;
  margin-bottom: 2px;
}


.pitch-header {
  text-align: center;
  padding: 3px 6px;
  border-radius: 3px;
  font-weight: bold;
  font-size: 10px;
  margin-bottom: 2px;
}

.footer {
  margin-top: 5px;
  padding-top: 3px;
  border-top: 1px solid #e2e8f0;
  font-size: 9px;
  color: #718096;
  text-align: center;
}
</style>

```{r header, results='asis', echo=FALSE}
cat('<div class="header-box">')
split_text <- if (params$split == "Left") "vs LHH" else "vs RHH"
cat(sprintf('<h1>%s <span style="font-size:11px; font-weight:normal; opacity:0.85;">| %s</span> <span style="font-size:11px; background:rgba(255,255,255,0.2); border-radius:3px; padding:1px 6px; margin-left:4px;">%s</span></h1>',
            params$pitcher, params$team, split_text))
cat('</div>')
```

<!-- Main content area -->
<div class="no-break">

<!-- Top section: 3-column layout -->
<table style="width: 100%; border-collapse: collapse; margin-bottom: 5px;">
<tr>

<!-- LEFT COLUMN: Pitcher image, ext, rel, grade, out pitch (~18%) -->
<td style="width: 18%; vertical-align: top; padding-right: 6px; border-right: 1px solid #e2e8f0;">

```{r left-pitcher-image, results='asis', echo=FALSE}
if (!is.null(params$pitcher_image) && params$pitcher_image != "") {
  cat(sprintf('<div style="text-align:center; margin-bottom:4px;"><img src="%s" style="width:100%%; max-width:90px; height:110px; object-fit:cover; border-radius:4px; border:1px solid #1a365d;" /></div>', params$pitcher_image))
} else {
  cat('<div style="width:100%; height:70px; background:#eee; border-radius:4px; display:flex; align-items:center; justify-content:center; font-size:7px; color:#888; margin-bottom:4px; text-align:center;">No image</div>')
}
```

```{r mech-colors, include=FALSE}
ext_color    <- get_mech_color(as.numeric(pitcher_info$extension))
rel_ht_color <- get_mech_color(as.numeric(pitcher_info$rel_height))
```

<div style="display:flex; gap:3px; margin-bottom:3px;">
<div class="stat-box" style="flex:1; margin-bottom:0; background:`r ext_color$bg`; color:`r ext_color$text`;"><div class="stat-label">EXT</div><div class="stat-value">`r pitcher_info$extension`</div></div>
<div class="stat-box" style="flex:1; margin-bottom:0; background:`r rel_ht_color$bg`; color:`r rel_ht_color$text`;"><div class="stat-label">REL HT</div><div class="stat-value">`r pitcher_info$rel_height`</div></div>
</div>

```{r left-grade, results='asis', echo=FALSE}
grade_val <- if (!is.null(params$grade) && params$grade != "") params$grade else ""
out_pitch_val <- if (!is.null(params$out_pitch) && params$out_pitch != "") params$out_pitch else ""

cat('<div style="display:flex; gap:3px;">')
if (grade_val != "") {
  cat(sprintf('<div class="grade-box" style="flex:1; margin-bottom:0;"><div class="grade-label">MIX</div><div class="grade-value">%s</div></div>', grade_val))
} else {
  cat('<div class="grade-box" style="flex:1; margin-bottom:0;"><div class="grade-label">MIX</div><div class="grade-value" style="color:#aaa;">—</div></div>')
}
if (out_pitch_val != "") {
  cat(sprintf('<div class="grade-box" style="flex:1; margin-bottom:0;"><div class="grade-label">OUT PITCH</div><div class="grade-value">%s</div></div>', out_pitch_val))
} else {
  cat('<div class="grade-box" style="flex:1; margin-bottom:0;"><div class="grade-label">OUT PITCH</div><div class="grade-value" style="color:#aaa;">—</div></div>')
}
cat('</div>')
```

</td>

<!-- MIDDLE COLUMN: Pitch table + footer stats + Attack Notes (~50%) -->
<td style="width: 50%; vertical-align: top; padding: 0 6px;">

```{r arsenal-table, results='asis', echo=FALSE}
if (!is.null(params$arsenal) && nrow(params$arsenal) > 0) {
  pitch_descs <- params$pitch_descriptions
  if (!is.list(pitch_descs)) pitch_descs <- as.list(pitch_descs)
  stats <- params$pitcher_stats

  # Overall zone % for footer
  overall_zone <- if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
    calculate_zone_pct_report(params$pitch_data)
  } else NA_real_

  # Build table HTML manually for full control
  cat('<table class="arsenal-table">')
  cat('<thead><tr>')
  cat('<th>Pitch</th><th>Usage</th><th>Velo</th><th>Zone%</th><th>Type</th><th>IVB</th><th>HB</th><th>Shape</th>')
  cat('</tr></thead>')
  cat('<tbody>')

  for (i in seq_len(nrow(params$arsenal))) {
    pt <- params$arsenal$pitch_type[i]
    colors <- get_pitch_color(pt)
    badge <- sprintf('<span style="background:%s; color:%s; padding:1px 5px; border-radius:2px; font-weight:bold; font-size:8px;">%s</span>',
                     colors$bg, colors$text, pt)
    usage_pct <- paste0(params$arsenal$usage[i], "%")
    zone_val <- params$arsenal$zone_pct[i]
    zone_disp <- if (!is.na(zone_val) && zone_val < 40) {
      sprintf('<span style="color:darkred;font-weight:bold;">%s%%</span>', zone_val)
    } else {
      paste0(zone_val, "%")
    }
    desc <- ""
    if (!is.null(pitch_descs) && length(pitch_descs) > 0 && pt %in% names(pitch_descs)) {
      val <- pitch_descs[[pt]]
      if (!is.null(val) && length(val) > 0) desc <- as.character(val[1])
    }
    cat(sprintf('<tr><td>%s</td><td>%s</td><td>%s</td><td>%s</td><td>%s</td><td>%s</td><td>%s</td><td style="text-align:left;">%s</td></tr>',
                badge, usage_pct, params$arsenal$velo[i], zone_disp,
                badge,
                params$arsenal$ivb[i], params$arsenal$hb[i], htmltools::htmlEscape(desc)))
  }

  # Footer row: Overall Zone% + Stats
  has_stats <- !is.null(stats) && (stats$ip != "" || stats$era != "" || stats$k != "" || stats$bb != "")
  zone_footer <- if (!is.na(overall_zone)) paste0("Zone: ", overall_zone, "%") else "Zone: N/A"
  stats_str <- if (has_stats) {
    parts <- c()
    if (!is.null(stats$ip) && stats$ip != "") parts <- c(parts, paste0("IP: ", stats$ip))
    if (!is.null(stats$era) && stats$era != "") parts <- c(parts, paste0("ERA: ", stats$era))
    if (!is.null(stats$k) && stats$k != "") parts <- c(parts, paste0("K: ", stats$k))
    if (!is.null(stats$bb) && stats$bb != "") parts <- c(parts, paste0("BB: ", stats$bb))
    if (params$split == "Left"  && !is.null(stats$baa_lhh) && stats$baa_lhh != "") parts <- c(parts, paste0("BAA-L: ", stats$baa_lhh))
    if (params$split == "Right" && !is.null(stats$baa_rhh) && stats$baa_rhh != "") parts <- c(parts, paste0("BAA-R: ", stats$baa_rhh))
    paste(parts, collapse = "  |  ")
  } else ""

  footer_text <- if (stats_str != "") paste0(zone_footer, "  |  ", stats_str) else zone_footer
  cat(sprintf('<tr class="footer-row"><td colspan="8" style="text-align:left; padding: 3px 4px;">%s</td></tr>', footer_text))

  cat('</tbody></table>')
}
```

```{r attack-notes, results='asis', echo=FALSE}
# Gameplan section fills lower half of middle column
gameplan_val <- if (!is.null(params$notes$gameplan) && params$notes$gameplan != "") params$notes$gameplan else ""
cat('<div style="background:#fffbeb; border:1px solid #f6e05e; border-radius:3px; padding:4px 6px; margin-top:4px; min-height:60px;">')
cat('<div style="font-weight:bold; color:#744210; font-size:8px; margin-bottom:4px;">GAMEPLAN</div>')
cat(sprintf('<div style="font-size:8px; line-height:1.4; white-space:pre-wrap; color:#1a202c;">%s</div>',
            if (gameplan_val != "") htmltools::htmlEscape(gameplan_val) else "\u2014"))
cat('</div>')
```

</td>

<!-- RIGHT COLUMN: Damage + Swing & Miss heatmaps (~32%) -->
<td style="width: 32%; vertical-align: top; padding-left: 6px; border-left: 1px solid #e2e8f0;">

<table style="width: 100%; border-collapse: collapse;">
<tr>
<td style="width: 50%; text-align: center; vertical-align: top; padding: 0 2px;">
<div class="heatmap-label">DAMAGE</div>
```{r damage-heatmap, fig.height=1.4, fig.width=1.4, out.width="98%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  generate_slg_heatmap_report(params$pitch_data, "")
}
```
</td>
<td style="width: 50%; text-align: center; vertical-align: top; padding: 0 2px;">
<div class="heatmap-label">SWING &amp; MISS</div>
```{r whiff-heatmap, fig.height=1.4, fig.width=1.4, out.width="98%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  generate_whiff_heatmap_report(params$pitch_data, "")
}
```
</td>
</tr>
</table>

</td>
</tr>
</table>

</div>

<!-- Heatmap sections with colored headers -->
<div class="section-header">OVERALL ATTACK</div>
<div class="heatmap-row">
<div class="notes-box"><strong>Notes:</strong>`r if(!is.null(params$notes$attack) && params$notes$attack != "") params$notes$attack else ""`</div>
```{r overall-heatmaps, fig.height=1.6, fig.width=10, out.width="100%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data
  canonical_pts <- head(params$arsenal$pitch_type, 5)
  ncols <- length(canonical_pts)
  usage <- df |> count(pitch_type_display) |> mutate(pct = round(n / sum(n) * 100, 0))
  headers <- lapply(canonical_pts, function(pt) {
    row <- usage[usage$pitch_type_display == pt, ]
    if (nrow(row) > 0) make_header_grob(pt, row$pct[1]) else make_blank_grob()
  })
  plots <- lapply(canonical_pts, function(pt) {
    row <- usage[usage$pitch_type_display == pt, ]
    if (nrow(row) > 0) generate_heatmap_pdf(df, pt, "") else make_blank_grob()
  })
  gridExtra::grid.arrange(grobs = c(headers, plots), ncol = ncols, nrow = 2,
    heights = grid::unit(c(0.22, 1.3), "in"))
}
```
</div>

<div class="section-header">FIRST PITCH (0-0)</div>
<div class="heatmap-row">
<div class="notes-box"><strong>Notes:</strong>`r if(!is.null(params$notes$first_pitch) && params$notes$first_pitch != "") params$notes$first_pitch else ""`</div>
```{r first-pitch-heatmaps, fig.height=1.6, fig.width=10, out.width="100%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data |> filter(balls == 0 & strikes == 0)
  if (nrow(df) >= 3) {
    canonical_pts <- head(params$arsenal$pitch_type, 5)
    ncols <- length(canonical_pts)
    usage <- df |> count(pitch_type_display) |> mutate(pct = round(n / sum(n) * 100, 0))
    headers <- lapply(canonical_pts, function(pt) {
      row <- usage[usage$pitch_type_display == pt, ]
      if (nrow(row) > 0) make_header_grob(pt, row$pct[1]) else make_header_grob(pt)
    })
    plots <- lapply(canonical_pts, function(pt) {
      generate_heatmap_pdf(df, pt, "")
    })
    gridExtra::grid.arrange(grobs = c(headers, plots), ncol = ncols, nrow = 2,
      heights = grid::unit(c(0.22, 1.3), "in"))
  }
}
```
</div>

<div class="section-header">HITTER ADVANTAGE (1-0, 2-0, 2-1, 3-0, 3-1)</div>
<div class="heatmap-row">
<div class="notes-box"><strong>Notes:</strong>`r if(!is.null(params$notes$hitter_adv) && params$notes$hitter_adv != "") params$notes$hitter_adv else ""`</div>
```{r hitter-adv-heatmaps, fig.height=1.6, fig.width=10, out.width="100%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data |>
    filter((balls == 1 & strikes == 0) | (balls == 2 & strikes %in% c(0, 1)) | (balls == 3 & strikes %in% c(0, 1)))
  if (nrow(df) >= 3) {
    canonical_pts <- head(params$arsenal$pitch_type, 5)
    ncols <- length(canonical_pts)
    usage <- df |> count(pitch_type_display) |> mutate(pct = round(n / sum(n) * 100, 0))
    headers <- lapply(canonical_pts, function(pt) {
      row <- usage[usage$pitch_type_display == pt, ]
      if (nrow(row) > 0) make_header_grob(pt, row$pct[1]) else make_header_grob(pt)
    })
    plots <- lapply(canonical_pts, function(pt) {
      generate_heatmap_pdf(df, pt, "")
    })
    gridExtra::grid.arrange(grobs = c(headers, plots), ncol = ncols, nrow = 2,
      heights = grid::unit(c(0.22, 1.3), "in"))
  }
}
```
</div>

<div class="section-header">TWO STRIKES (2K)</div>
<div class="heatmap-row">
<div class="notes-box"><strong>Notes:</strong>`r if(!is.null(params$notes$two_k) && params$notes$two_k != "") params$notes$two_k else ""`</div>
```{r 2k-heatmaps, fig.height=1.6, fig.width=10, out.width="100%"}
if (!is.null(params$pitch_data) && nrow(params$pitch_data) > 0) {
  df <- params$pitch_data |> filter(strikes == 2)
  if (nrow(df) >= 3) {
    canonical_pts <- head(params$arsenal$pitch_type, 5)
    ncols <- length(canonical_pts)
    usage <- df |> count(pitch_type_display) |> mutate(pct = round(n / sum(n) * 100, 0))
    headers <- lapply(canonical_pts, function(pt) {
      row <- usage[usage$pitch_type_display == pt, ]
      if (nrow(row) > 0) make_header_grob(pt, row$pct[1]) else make_header_grob(pt)
    })
    plots <- lapply(canonical_pts, function(pt) {
      generate_heatmap_pdf(df, pt, "")
    })
    gridExtra::grid.arrange(grobs = c(headers, plots), ncol = ncols, nrow = 2,
      heights = grid::unit(c(0.22, 1.3), "in"))
  }
}
```
</div>

<div class="section-header">RISP (RUNNERS IN SCORING POSITION)</div>
<div class="heatmap-row">
<div class="notes-box"><strong>Notes:</strong>`r if(!is.null(params$notes$risp) && params$notes$risp != "") params$notes$risp else ""`</div>
<div style="flex: 1; display: flex; justify-content: flex-start; align-items: flex-start; gap: 8px;">
```{r risp-section, results='asis', echo=FALSE}
risp_imgs <- params$risp_images
if (!is.list(risp_imgs)) risp_imgs <- as.list(risp_imgs)

risp_usages <- params$risp_usages
if (!is.list(risp_usages)) risp_usages <- as.list(risp_usages)

# Get pitch order from arsenal
pitch_order <- if (!is.null(params$arsenal)) head(params$arsenal$pitch_type, 6) else names(risp_imgs)

if (length(pitch_order) > 0) {
  for (pt in pitch_order) {
    colors <- get_pitch_color(pt)

    # Get usage for this pitch
    usage_val <- if (pt %in% names(risp_usages)) {
      paste0(risp_usages[[pt]], "%")
    } else {
      ""
    }

    # Get image URL
    url <- ""
    if (pt %in% names(risp_imgs)) {
      url_val <- risp_imgs[[pt]]
      if (!is.null(url_val) && length(url_val) > 0) url <- as.character(url_val[1])
    }

    cat('<div style="flex: 1; max-width: 120px; text-align: center;">')

    # Colored header with pitch name and usage
    if (usage_val != "") {
      cat(sprintf('<div style="background: %s; color: %s; padding: 2px 4px; border-radius: 3px; font-weight: bold; font-size: 8px; margin-bottom: 2px;">%s (%s)</div>',
                  colors$bg, colors$text, pt, usage_val))
    } else {
      cat(sprintf('<div style="background: %s; color: %s; padding: 2px 4px; border-radius: 3px; font-weight: bold; font-size: 8px; margin-bottom: 2px;">%s</div>',
                  colors$bg, colors$text, pt))
    }

    # Image or placeholder
    if (url != "") {
      cat(sprintf('<img src="%s" style="width: 100%%; max-height: 70px; object-fit: contain; border: 1px solid #ddd; border-radius: 3px;"/>', url))
    } else {
      cat('<div style="height: 50px; background: #f5f5f5; border: 1px dashed #ccc; border-radius: 3px; display: flex; align-items: center; justify-content: center; font-size: 7px; color: #888;">No image</div>')
    }

    cat('</div>')
  }
} else {
  cat('<div style="color: #888; font-size: 8px; padding: 10px;">No RISP data</div>')
}
```
</div>
</div>

<div class="footer">
Report generated `r Sys.Date()` | Cal Poly Baseball | Print (Ctrl/Cmd + P) to save as PDF
</div>
